```{r}

```

# Loading

```{r}
library(readr)
Meals <- read_csv("Meals.csv", col_types = cols(`ORDER DATE` = col_date(format = "%d-%m-%Y"), 
    `ORDER NO` = col_skip(), `CUSTOMER NAME` = col_skip()))
attach(Meals)
```

## WeekDays

```{r}
Meals$Week.Day<-weekdays.POSIXt(`ORDER DATE`)
```

#### See if receiving coupons changes preferences of dining in and dining out

```{r}
chisq.test(table(`ORDER TYPE`,COUPON))

#stack_barplot
Order_type_coupon_p1 = ggplot(MorData, aes(x = `ORDER TYPE`, fill = COUPON)) + 
  geom_bar(position = "stack")
Order_type_coupon_p1
```

The **p-value=0.5396** so we **fail to reject** the Null Hypothesis. Coupons don't affect customer crowds inside restaurants.

### See if Origin city matters when you pay online

```{r}
chisq.test(table(`ORIGIN CITY`,`PAYMENT MODE`))

#stack_barplot
Origin_city_payment_p1 = ggplot(MorData, aes(x = `ORIGIN CITY`, fill = `PAYMENT MODE`)) + 
  geom_bar(position = "stack")
Origin_city_payment_p1

```

The **p-value=7.389e-06** so we **reject** the Null Hypothesis. Payment Modes are dependent on Origin City.

Chi Square test is not approximate for values less than 5. So our results are inconclusive.

### See if people in different states have different food Preferences

```{r}
chisq.test(table(STATE,CATEGORY))

#stack_barplot
State_category_p1 = ggplot(MorData, aes(x = STATE, fill = CATEGORY)) + 
  geom_bar(position = "stack")
State_category_p1
```

Here **p-value=2.644e-07** we reject the Null Hypothesis and say people from different states have different food preferences.

```{r}

chisq.test(table(CATEGORY, weekdays.Date(`ORDER DATE`)))

#stack_barplot
Category_order_date_p1 = ggplot(MorData, aes(x = CATEGORY, fill = weekdays.Date(`ORDER DATE`))) +
  geom_bar(position = "stack")
Category_order_date_p1
```

### People eat in and eat out regardless of coupons

```{r}
DineOrder=table(`ORDER TYPE`,COUPON)
DineOrder
marginSums(DineOrder,margin = 1)
marginSums(DineOrder,margin = 2)
#Dine in with reagrd to coupons
prop.test(x=c(132,52),n=c(405,145),alternative = "less")
#Coupons with regard to dineins
prop.test(x=c(132,273),n=c(184,366),alternative = "less")

#pie_chart
ggpiestats(
  data = MorData,
  x = `ORDER TYPE`,
  y = COUPON,
  label = "both",
  ggtheme = ggplot2::theme_linedraw(),
  plotgrid.args = list(nrow = 2)
)
```

```{r}
OrderPay=table(`ORDER TYPE`,`PAYMENT MODE`)
OrderPay
marginSums(OrderPay,margin = 1)
marginSums(OrderPay,margin = 2)
#Dine in with reagrd to coupons
prop.test(x=c(299,97),n=c(405,145),alternative = "greater",conf.level = 0.93)

#stack_barplot
Origin_type_payment_p1 = ggplot(MorData, aes(x = `ORDER TYPE`, fill = `PAYMENT MODE`)) + 
  geom_bar(position = "stack")
Origin_type_payment_p1

#pie_chart
ggpiestats(
  data = MorData,
  x = `ORDER TYPE`,
  y = `PAYMENT MODE`,
  label = "both",
  ggtheme = ggplot2::theme_linedraw(),
  plotgrid.args = list(nrow = 2)
)

```

At **conf level=0.93 p-value=0.06848** we reject Null Hypothesis and conclude proportion for people who use cash mode of payment is more than for proportion of people who use digital payment.

```{r}
table(`PAYMENT MODE`)
prop.test(154,550,alternative = "less")

#pie_chart
ggpiestats(
  data = MorData,
  x = `PAYMENT MODE`,
  label = "both",
  ggtheme = ggplot2::theme_linedraw(),
  plotgrid.args = list(nrow = 2)
)
```

Here we reject NULL Hypothesis and say that people prefer cash payments compared to digital payments

```{r}
chisq.test(table(STATE,`PAYMENT MODE`))

#pie_chart
ggpiestats(
  data = MorData,
  x = `PAYMENT MODE`,
  y = STATE,
  label = "both",
  ggtheme = ggplot2::theme_linedraw(),
  plotgrid.args = list(nrow = 2)
)
```
